Overview

### 2023-12-07 analysis/001_overview.Rmd
Subject overview table

>>>>

Here's a table. I applied fractional counting because of large overlaps.

```{r subject_summary_table}
jn_fract <- subject_df |>
  # with at least one
  filter(oa > 0) |>
  distinct(issn_l, top_level) |>
  group_by(issn_l, top_level) |>
  summarise(n = n_distinct(issn_l)) |>
  mutate(fractions_factor = n / sum(n)) |>
  mutate(fractions = n * fractions_factor) |>
  ungroup() |> 
  group_by(top_level) |>
  summarise(jn_frac = sum(fractions)) |>
  arrange(top_level)

subject_tbl <- top_level_by_year_oa |>
  inner_join(jn_fract, by = "top_level") |>
  filter(!top_level %in% c("Multidisciplinary", NA)) |>
  group_by(top_level, jn_frac) |>
  summarise(articles_frac = sum(articles_frac),
            oa_frac = sum(oa_frac),
            ta_oa_frac = sum(ta_oa_frac)) |>
  ungroup() |>
  mutate(
    jn_perc = jn_frac / sum(jn_frac),
    jn_cum = cumsum(jn_frac) / sum(jn_frac),
    perc = articles_frac / sum(articles_frac),
    cum = cumsum(articles_frac) / sum(articles_frac),
    oa_perc = oa_frac / sum(oa_frac),
    oa_cum = cumsum(oa_frac) / sum(oa_frac),
    ta_oa_perc = ta_oa_frac / sum(ta_oa_frac),
    ta_oa_cum = cumsum(ta_oa_frac) / sum(ta_oa_frac)
  ) |>
  select(top_level, jn_frac, jn_perc, jn_cum, articles_frac, perc, cum, 
         oa_frac, oa_perc, oa_cum, ta_oa_frac,ta_oa_perc,  ta_oa_cum)

subject_tbl |>
  mutate(across(contains(c("perc", "cum")), ~ paste(round(., 3) * 100))) |>
  kbl(
    caption ="Hybrid open access through transformative agreements by journal subject 2018-2022",
    col.names = c(
      "Journal subject",
      "Total",
      "%",
      "C%",
      "Total",
      "%",
      "C%",
      "Total",
      "%",
      "C%",
      "Total",
      "%",
      "C%"
    ),
    format.args = list(big.mark = ',')
  ) %>%
  kable_classic() %>%
  add_header_above(c(
    " " = 1,
    "Hybrid journals" = 3,
    "Articles" = 3,
    "OA articles" = 3,
    "TA OA articles" = 3
  ))
```
